Evolution of Methodologies in Delivering Reliable Software in the European Scientific Arena

### 2018-06-01 paper-ieee-trans.tex
update fig3, and Rscript

\begin{figure*}[ht]
\centering
\includegraphics[width=\textwidth]{images/fig2.png}
%\includegraphics[width=0.8\textwidth]{images/fig2a.pdf}
\caption{Comparison of the unit testing coverage values for the {\sl INDIGO--DataCloud} software stack over the {\sl INDIGO--1} and {\sl INDIGO--2} major releases.}
\label{fig:fig_unittest}
\end{figure*}

\begin{figure*}[ht]
\centering
\includegraphics[width=0.8\textwidth]{images/fig3.png}
\caption{Trend line showing the adoption of Configuration Management tools throughout the project lifetime.}
\label{fig:fig_confman}
\end{figure*}

@@

\item \textit{Automated Deployment}.
To lower the barriers of software adoption, the SQA criteria require the automated
deployment of the products delivered as part of the catalogue. Automation in this context is
tackled using a configuration management tool. These tools allow to have an
\textit{Infrastructure as Code} (IaC), managing the component's deployment through declarative
definitions. The definition files appear as additional source of documentation
-- self--documenting code -- as they sequentially guide the component's deployment process in multiple
platforms. {\sl INDIGO--DataCloud} project contributed to open--source IaC tools such
as Ansible \cite{indigo-galaxy} and Puppet \cite{indigo-puppet}. A representative example of
such contribution are the \textit{50 roles} being developed from scratch, currently hosted in
the Ansible Galaxy portal \cite{indigo-galaxy}. Fig.~\ref{fig:fig_confman}
shows the number of products that offer an automated means for deployment.
It shows an increase after the {\sl INDIGO--1} release and in the previous weeks of each
of the two major releases.
\end{itemize}

@@

\bibitem{iso-9126}
\emph{ISO/IEC 9126 Software Engineering - Product Quality}, International
Organization for Standarization [Online]. Available: https://www.iso.org/standard/22749.html .

@@

\bibitem{indigo-github}
\emph{INDIGO--DataCloud GitHub Source Code repository} [Online]. Available:
https://www.github.com/indigo-dc

>>>>

\begin{figure*}[ht]
\centering
\includegraphics[width=\textwidth]{images/fig2.png}
\caption{Comparison of the unit testing coverage values for the {\sl INDIGO--DataCloud} software stack over the {\sl INDIGO--1} and {\sl INDIGO--2} major releases.}
\label{fig:fig_unittest}
\end{figure*}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{images/fig3.png}
\caption{Adoption of Configuration Management tools throughout the project lifetime. Also shown the trend lines
leading to the first release (dark blue points and lines), and to the second release (light cream points and lines).}
\label{fig:fig_confman}
\end{figure}

@@

\item \textit{Automated Deployment}.
To lower the barriers of software adoption, the SQA criteria require the automated
deployment of the products delivered as part of the catalogue. Automation in this context is
tackled using a configuration management tool. These tools allow the adoption of
\textit{Infrastructure as Code} (IaC), managing the component's deployment through declarative
definitions. The definition files appear as additional source of documentation
-- self--documenting code -- as they sequentially guide the component's deployment process in multiple
platforms. {\sl INDIGO--DataCloud} project contributed to open--source IaC tools such
as Ansible \cite{indigo-galaxy} and Puppet \cite{indigo-puppet}. A representative example of
such contribution are the \textit{50 roles} developed from scratch and currently hosted in
the Ansible Galaxy portal \cite{indigo-galaxy}. Fig.~\ref{fig:fig_confman}
shows the number of products that offer an automated means for deployment.
It shows an increase in the adoption of such tools leading to the {\sl INDIGO--1} release
(dark blue points and trend line), as well as to the {\sl INDIGO--2} release
(light cream points and trend line). The rate of adoption is lower during the weeks
before the second release because a significant fraction of the products had already adopted it
previously to the first release.
\end{itemize}

@@

\bibitem{iso-9126}
\emph{ISO/IEC 9126 Software Engineering - Product Quality}, International
Organization for Standardization [Online]. Available: https://www.iso.org/standard/22749.html .

@@

\bibitem{indigo-github}
\emph{INDIGO--DataCloud GitHub Source Code repository} [Online]. Available:
https://www.github.com/indigo-dc .
